Rigid fluid coupling

### 2022-05-10 manuscript/paper.tex
Working stack of cylinders with corrected Mohseni force law.

\usepackage{caption}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{cleveref}

@@

\section{Introduction}
\label{sec:intro}

\section{Governing equations}
\label{sec:fluid-mechanics}

\section{CTVF formulation}
\label{sec:ctvf-equations}

\section{SPH discretization}
\label{sec:sph-fluid-equations}

\section{Rigid body dynamics}
\label{sec:rbd}

\section{How to handle rigid fluid coupling}
\label{sec:rfc}

\section{Collision between rigid bodies}
\label{sec:contact-force}

@@

\section{Results and discussion}
\label{sec:results}

@@

\Cref{fig:dinesh-2022-bouncing-cube-snapshots-3d} depicts the snapshots of the
rigid body bouncing on a wall. The coefficient of restitution corresponding to
the snapshots are equal to $1$. As the rigid body approaches the wall, its
velocity is increases due to gravity. As soon as the body comes into contact
of the wall, the collision happens, the body's velocity is reduced until it
becomes zero, and then it rebounds, and bounces back to a certain height.

\begin{figure}[!htpb]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time0}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-0}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time1}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-1}
  \end{subfigure}

  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time2}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-2}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time3}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-3}
  \end{subfigure}
  \caption{Elastic solid sliding}
\label{fig:mohseni-2021-sliding-3d}
\end{figure}
%

\subsubsection{A test to check the conservation properties of rigid body}
\label{sec:conservation-of-rb-properties}

\subsection{A 2d and 3d rigid body sliding}
\label{sec:rigid-body-sliding}

@@

\begin{figure}[!htpb]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time0}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-0}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time1}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-1}
  \end{subfigure}

  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time2}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-2}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_4/time3}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-3}
  \end{subfigure}
  \caption{Elastic solid sliding}
\label{fig:mohseni-2021-sliding-3d}
\end{figure}
%

@@

\subsection{Controlled Sliding on a Flat Surface}
\label{sec:controlled-rigid-body-sliding}

\subsection{Stack of cylinders}
\label{sec:stack-of-cylinders}

\subsection{Falling solid in water}
\label{sec:falling-solid-in-water}

\subsection{Floating solid in water}
\label{sec:floating-solid-in-water}

\subsection{3D dam breaking flow hitting one cube}
\label{sec:3d-dam-breaking-one-cube-hit}

>>>>

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{relsize}
\usepackage[utf8]{inputenc}
\usepackage{cleveref}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[section]{placeins}
\usepackage{booktabs}

@@

\section{Introduction}
\label{sec:intro}
\begin{itemize}
\item Rigid bodies in fluid flows in nature. Where can we find them? What kind
  of problems do they give rise to? Ice-Sea? Debris?
\item Many different ways RFC is been modeled, this includes mesh based and
  mess less. Explain in a good detail what meshless methods are out there
  which handles these problems. This includes SPH too.
\item Explain SPH history and its applications in different areas. Now SPH
  specifically applied in RFC area. Detail some papers where how differently
  fluid is modelled, this includes ISPH, WCSPH, TVF, delta+ SPH. Also mention
  the latest multiphase flow, where air is considered, then mention the
  adaptive formulation, where the author captures the cavity.
\item Similarly explain the many ways the rigid-rigid coupling is been
  handled. Detail how non-smooth boundaries are handled.
\item Mention the open source software which provide SPH formulation (there are 2.)
\item Explain what we are going to do in the current work. We adapt the
  Mohseni formulation to handle the non-smooth boundaries, we also incorporate
  the damping, and extend the formulation to 3d and simulate 3d problems.
\item Explain the examples. 3d Sliding case, 3d controlled sliding case, body
  falling in water, then 3d dam break over dynamics rigid obstacles.
\end{itemize}

\FloatBarrier%
\section{Fluid dynamics}
\label{sec:fluid-dynamics}

\todoin{Connor FSI}

The mass and momentum conservation laws that govern the dynamics of fluid motion are given in Lagrangian form by:
\begin{equation}
  \label{eq:ce}
  \frac{d \rho}{d t} = - \rho \; \frac{\partial u_i}{\partial x_i},
\end{equation}
\begin{equation}
  \label{eq:me}
  \frac{d u_i}{d t} = \frac{1}{\rho} \; \frac{\partial \sigma_{ij}}{\partial x_j}
  + g_i,
\end{equation}
where $\rho$ is the density, $u_i$ is the $i$\textsuperscript{th} component of
the velocity field, $x_j$ is the $j$\textsuperscript{th} component of the
position vector, $g_i$ is the component of body force per unit mass. And $\frac{d}{d t}$ is
\begin{equation}
  \label{eq:material-derivative}
  \frac{d}{d t} = \frac{\partial }{\partial t} +
  {u}_j \frac{\partial }{\partial x_j}.
\end{equation}

Following CTVF formulation, and moving the particles with transport velocity,
we have the modified material derivative as
\begin{equation}
  \label{eq:modified-material-derivative}
  \frac{\tilde{d} }{d t} = \frac{\partial }{\partial t} +
  \tilde{u}_j \frac{\partial }{\partial x_j}.
\end{equation}

The adjust equations for the modified derivative are given by:

\begin{equation}
  \label{eq:ce-tvf}
  \frac{\tilde{d} \rho}{d t} =
  - \rho \frac{\partial \tilde{u}_j}{\partial x_j} +
  \frac{\partial (\rho (\tilde{u}_j - u_j))}{\partial x_j}.
\end{equation}
\begin{equation}
  \label{eq:mom-tvf}
  \frac{\tilde{d} u_i}{d t} =
  \frac{\partial}{\partial x_j} (u_i (\tilde{u}_j - u_j))
  - u_i \frac{\partial}{\partial x_j} (\tilde{u}_j - u_j)
  + g_i
  +\frac{1}{\rho} \frac{\partial \sigma_{ij}}{\partial x_j}.
\end{equation}

For a weakly-compressible or incompressible fluid, a viscous force is added:
\begin{equation}
  \label{eq:fluid-stress-decomposition}
  \sigma_{ij} = - p \delta_{ij} + 2 \eta \frac{\partial u_i}{\partial x_j}
\end{equation}
where $\eta$ is the kinematic viscosity of the fluid.

In both fluid and solid modelling the pressure is computed using an
isothermal equation of state, given as,
\begin{equation}
  \label{eq:pressure-equation}
  p = K \bigg(\frac{\rho}{\rho_{0}} - 1 \bigg),
\end{equation}
where $K = \rho_{0} c_0^2$ is the bulk modulus. Here, the constants $c_0$ and
$\rho_0$ are the reference speed of sound and density, respectively. For solids,
$c_0$ is computed as $\sqrt{\frac{E}{3 (1 - 2 \nu)\rho_{0}}}$, $\nu$ is the
Poisson ratio.

SPH discretization of the modified governing equations are given by:
\begin{equation}
  \label{eq:sph-discretization-continuity}
  \frac{\tilde{d}\rho_a}{dt} = \sum_{b} \; \frac{m_b}{\rho_{b}} \; (
  \rho_{a} \; \tilde{\ten{u}}_{ab} \; + \;
  (\rho \; (\tilde{\ten{u}} \; - \;
  \ten{u}))_{ab}) \; \cdot \nabla_{a} W_{ab},
\end{equation}
\begin{multline}
  \label{eq:sph-momentum-fluid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
  \bigg) \bigg]
  \cdot \nabla_{a} W_{ab} \\
  + \ten{u}_{a} \sum_{b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
  \nabla_{a} W_{ab} + \sum_{b} m_b \frac{4 \eta \nabla W_{ab}\cdot
    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} +
  \ten{g}_{a},
\end{multline}
The particles in the current scheme are moved with the transport velocity,
\begin{equation}
  \label{eq:transport_velocity_position_derivative}
  \frac{d\ten{r}_a}{dt} = \ten{\tilde{u}}_a.
\end{equation}
%
The transport velocity is updated using,
\begin{equation}
  \label{eq:transport_velocity}
  \ten{\tilde{u}}_a(t + \Delta t) =\ten{u}_a(t) + \Delta t \; \frac{\tilde{d} \ten{u}_a}{dt} +
  \bigg(\frac{d \ten{u}_{a}}{dt}\bigg)_{\text{c}} \Delta t,
\end{equation}
where $\ten{A}_a = \rho_a \ten{u}_a \otimes (\ten{\tilde{u}}_a - \ten{u}_a)$,
$\ten{I}$ is the identity matrix, $\eta$ is the kinematic viscosity of the
fluid and \citet{morris1997modeling} formulation is used to discretize the
viscosity term.
\begin{itemize}
\item Discuss about the homogenization force (We use GTVf).
\item Describe $\Pi_{ij}$ for numerical stability.
\item And other terms.
\end{itemize}
We add to the momentum equation an additional artificial viscosity term
$\Pi_{ab}$~\cite{monaghan-review:2005} to maintain the stability of the
numerical scheme, given as,
\begin{align}
  \label{eq:mom-av}
  \Pi_{ab} =
  \begin{cases}
\frac{-\alpha h_{ab} \bar{c}_{ab} \phi_{ab}}{\bar{\rho}_{ab}}
  & \ten{u}_{ab}\cdot \ten{r}_{ab} < 0, \\
  0 & \ten{u}_{ab}\cdot \ten{r}_{ab} \ge 0,
\end{cases}
\end{align}
where,
%
\begin{equation}
  \label{eq:av-phiij}
  \phi_{ab} = \frac{\ten{u}_{ab} \cdot \ten{r}_{ab}}{r^2_{ab} + 0.01 h^2_{ab}},
\end{equation}
%
where $\ten{r}_{ab} = \ten{r}_a - \ten{r}_b$, $\ten{u}_{ab} = \ten{u}_a -
\ten{u}_b$, $h_{ab} = (h_a + h_b)/2$, $\bar{\rho}_{ab} = (\rho_a + \rho_b)/2$,
$\bar{c}_{ab} = (c_a + c_b) / 2$, and $\alpha$ is the artificial
viscosity parameter.

%
where $\big(\frac{d \ten{u}_a}{dt}\big)_{\text{c}}$ is the homogenization
acceleration which ensures that the particle positions are homogeneous.

\subsection{Boundary conditions}

The ghost particle approach of \citet{Adami2012} is used to model the
boundaries. We use three layers of ghost particles to model the solid wall.
The properties of the solid wall are interpolated from the fluid particles.

When computing the divergence of the velocity field on fluid particles, we
enforce a no-penetration boundary condition and not a no-slip boundary
condition. The velocity of the fluid is projected onto the ghost particles
using,
\begin{equation}
  \label{eq:v-ghost}
  \ten{\hat{u}}_a = \frac{\sum_b\ten{u}_b W_{ab}}{\sum_b W_{ab}},
\end{equation}
\begin{equation}
  \label{eq:v-hat-ghost}
  \ten{\check{u}}_a = \frac{\sum_b\tilde{\ten{u}}_b W_{ab}}{\sum_b W_{ab}},
\end{equation}
where $\ten{u}_b$, $\ten{\tilde{u}}_b$ are the momentum and transport velocity
of the fluid respectively and $W_{ab}$ is the kernel value between the fluid
particle and the ghost particle.

The normal component of this projected velocity is then reflected and set as
the ghost particle velocity,
\begin{equation}
  \label{eq:free-slip-bc-u}
  \ten{u}_{\text{Ga}} = 2 \ten{\hat{n}}((\ten{u}_{\text{p}} - \ten{\hat{u}}_{\text{a}})\cdot \ten{\hat{n}}) + \ten{\hat{u}}_{\text{a}},
\end{equation}
where $\ten{u}_{\text{p}}$ is the local velocity of the boundary and
$\ten{\hat{n}}$ is the unit normal to the boundary particle $a$. Similarly the
transport velocity of the ghost particle is set as,
\begin{equation}
  \label{eq:free-slip-bc-u}
  \tilde{\ten{u}}_{\text{Gi}} = 2 \ten{\hat{n}}((\ten{u}_{\text{p}} - \ten{\check{u}}_{\text{i}})\cdot \ten{\hat{n}}) + \ten{\check{u}}_{\text{i}},
\end{equation}

When the viscous force is computed, the no slip boundary condition is used,
where the velocity on the boundary set as,
\begin{equation}
  \label{eq:no-slip-bc-u}
  \ten{u}_{\text{Ga}} = 2 \ten{u}_{\text{p}} - \ten{\hat{u}}_{\text{a}},
\end{equation}
a similar form is used for the transport velocity here too,
\begin{equation}
  \label{eq:no-slip-bc-uhat}
  \tilde{\ten{u}}_{\text{Ga}} = 2 \ten{u}_{\text{p}} - \ten{\check{u}}_{\text{a}}.
\end{equation}

The pressure of the boundary particle is extrapolated from its surrounding
fluid particles by the following equation,
\begin{equation}
  \label{eq:pressure-bc}
  p_w = \frac{\Sigma_f p_f W_{wf} + (\ten{g} - \ten{a}_{\ten{w}}) \cdot \Sigma_f
    \rho_f \ten{r}_{wf} W_{wf}}{\Sigma_f W_{wf}},
\end{equation}
where $\ten{a}_w$ is the acceleration of the wall. The subscript $f$ denotes
the fluid particles and $w$ denotes the wall particles.

\begin{itemize}
\item Choose the timestep
\end{itemize}

\FloatBarrier%
\section{Rigid body dynamics}
\label{sec:rbd}

The state of a rigid body is defined by position of center of mass, velocity
of center of mass, a rotation matrix to define the three rotational degrees of
freedom and angular velocity.

The equations governing the dynamics of rigid body are, balance of linear and
angular momentum given by,

\begin{equation}
  \label{eq:balance_linear_mom}
  \frac{d \; (M \ten{v}_{cm})}{d t} = \sum_i \ten{F}_i
\end{equation}

\begin{equation}
  \label{eq:balance_angular_mom}
  \frac{d \ten{L}}{d t} = \teng{\tau}_{cm}
\end{equation}

where $\teng{\tau}_i$ is the torque about center of mass due to forces on the
particles,

\begin{equation}
  \label{eq:torque}
  \teng{\tau}_{cm} = \sum_i \ten{F}_i \times (\ten{r}_{cm} - \ten{r}_{i})
\end{equation}

The angular momentum and the center of mass velocity of the body is updated by following

\begin{equation}
  \label{eq:ang_mom_update}
  \ten{x}_{cm} = \ten{x}_{cm} + \frac{\ten{F}_{cm}}{M} \; \Delta t
\end{equation}

\begin{equation}
  \label{eq:ang_mom_update}
  \ten{L} = \ten{L} + \teng{\tau}_{cm} \; \Delta t
\end{equation}

\begin{equation}
  \label{eq:rotation_update}
  \ten{R} = \ten{R} + \tilde{\teng{\omega}} \, \ten{R} \; \Delta t
\end{equation}

\begin{equation}
  \label{eq:moi_update}
  \ten{I}^{-1} = \ten{R} \hat{\ten{I}}^{-1} \ten{R}^T
\end{equation}

\begin{equation}
  \label{eq:moi_update}
  \teng{\omega} = \ten{I}^{-1} \; \ten{L}
\end{equation}

Particles update

\begin{equation}
  \label{eq:rb_particle_pos_update}
  \ten{x}_i(t) = \ten{x}_{cm}(t) + \ten{R}(t) \; \hat{\ten{r}}_{i}(t)
\end{equation}

\begin{equation}
  \label{eq:rb_particle_vel_update}
  \ten{v}_i(t) = \ten{v}_{cm}(t) + \teng{\omega}(t) \; \ten{r}_{i}(t)
\end{equation}

\FloatBarrier%
\section{Rigid fluid coupling}
\label{sec:rfc}

In order to find the forces on rigid body due to fluid and vice versa, we
assume the particles of rigid body to be dummy and consider a hydrodynamic
mass attach to it. A three layers of particles are expected on the rigid body
and the force acting on the fluid due to the

\begin{multline}
  \label{eq:force_on_fluid_due_to_rb}
  \frac{\tilde{d}\ten{u}_{a}}{dt} =  \sum_{b} m^0_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I}\bigg) \bigg]
  \cdot \nabla_{a} W_{ab}
\end{multline}

\begin{multline}
  \label{eq:force_on_fluid_due_to_rb}
  f_i =  m_a \sum_{b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I}\bigg) \bigg]
  \cdot \nabla_{a} W_{ab}
\end{multline}

The pressure on the rigid body is computed using the Adami boundary condition.
Similarly we set no slip velocity condition for the computation of viscous
force computation.

\FloatBarrier%
\section{Collision between rigid bodies}
\label{sec:contact-force}

@@

\FloatBarrier%
\section{Final set of governing equations}
\label{sec:final_discretized_equations}

\begin{itemize}
\item Write the time step factor.
\item Write the rigid body equations with real forces.
\item Write rigid body particle equations.
\end{itemize}

\begin{multline}
  \label{eq:sph-momentum-fluid}
  \frac{\tilde{d}\ten{u}_{a}}{dt} = - \sum_{b \in b_f} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
  \bigg) + \Pi_{ab} \bigg]
  \cdot \nabla_{a} W_{ab} \\
  + \ten{u}_{a} \sum_{b \in b_f} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
  \nabla_{a} W_{ab} + \sum_{b \in b_f} m_b \frac{4 \eta \nabla W_{ab}\cdot
    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab} \\
 - \sum_{b \in b_r} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
  \bigg) + \Pi_{ab} \bigg]
  \cdot \nabla_{a} W_{ab} \\
  + \ten{u}_{a} \sum_{b \in b_r} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
  \nabla_{a} W_{ab} + \sum_{b \in b_r} m_b \frac{4 \eta \nabla W_{ab}\cdot
    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab}\\
 - \sum_{b \in b_b} m_b \bigg[
  \bigg(\frac{p_a}{\rho_a^2} + \frac{p_b}{\rho_b^2}\bigg) \ten{I} -
  \bigg(\frac{\ten{A}_a}{\rho_a^2} + \frac{\ten{A}_b}{\rho_b^2}
  \bigg) + \Pi_{ab} \bigg]
  \cdot \nabla_{a} W_{ab} \\
  + \ten{u}_{a} \sum_{b \in b_b} \frac{m_b}{\rho_{b}} \; \tilde{\ten{u}}_{ab} \cdot
  \nabla_{a} W_{ab} + \sum_{b \in b_b} m_b \frac{4 \eta \nabla W_{ab}\cdot
    \ten{r}_{ab}}{(\rho_a + \rho_b) (r_{ab}^2 + 0.01 h_{ab}^2)} \ten{u}_{ab}
  + \ten{g}_{a}
\end{multline}

The particles in the current scheme are moved with the transport velocity,
\begin{equation}
  \label{eq:transport_velocity_position_derivative}
  \frac{d\ten{r}_a}{dt} = \ten{\tilde{u}}_a.
\end{equation}

\todoin{Rigid body equations}
\todoin{Expand on forces in detail}
\begin{equation}
  \label{eq:balance_linear_mom}
  \frac{d \; (M \ten{v}_{cm})}{d t} = \sum_i \ten{F}_{due to fluid} \sum_i \ten{F}_{due to solids}
\end{equation}

\begin{equation}
  \label{eq:balance_angular_mom}
  \frac{d \ten{L}}{d t} = \sum_i \ten{F}_{due to fluid} \sum_i \ten{F}_{due to solids} \times (\ten{r}_{cm} - \ten{r}_{i})
\end{equation}

\begin{equation}
  \label{eq:rb_particle_pos_update}
  \ten{x}_i(t) = \ten{x}_{cm}(t) + \ten{R}(t) \; \hat{\ten{r}}_{i}(t)
\end{equation}

\begin{equation}
  \label{eq:rb_particle_vel_update}
  \ten{v}_i(t) = \ten{v}_{cm}(t) + \teng{\omega}(t) \; \ten{r}_{i}(t)
\end{equation}

\FloatBarrier%
\section{Results and discussion}
\label{sec:results}

@@

\FloatBarrier%
\subsection{A 2d and 3d rigid body sliding}
\label{sec:rigid-body-sliding}

@@

\begin{figure}[!htpb]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_2/time0}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-0}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_2/time1}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-1}
  \end{subfigure}

  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/fric_coeff_0_2/time2}
    \subcaption{t = 2.5e-03 sec}\label{fig:passing-2}
  \end{subfigure}
  \caption{Rigid body with friction $0.2$ sliding.}
\label{fig:mohseni-2021-sliding-3d}
\end{figure}

@@

\FloatBarrier%
\subsection{Controlled Sliding on a Flat Surface}
\label{sec:controlled-rigid-body-sliding}

In the current section we control a rigid body to slide on a frictional flat
surface by applying an external normal $F_n$ and tangential force $F_t$. The
friction coefficient between the body and wall is assumed to be $0.5$. The
schematic of the rigid body as well as the wall is shown in
\cref{fig:schematic-controlled-rigid-body-sliding}.
\begin{figure}[!htpb]
  \centering
  % \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Schematic of the controlled rigid body sliding}
\label{fig:schematic-controlled-rigid-body-sliding}
\end{figure}

\Cref{fig:velocity-vs-time-controlled-sliding} depicts the time histories of
velocity of the center of mass of the rigid body with time, as well as the
variation of applied external normal $F_n$ and tangential $F_t$ forces.
\begin{itemize}
\item How the normal force is varied?
\item When does the tangential force come into picture?
\item What physics is supposed to follow?
\item Say that the current velocity variation is matching with the analytical one.
\end{itemize}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Velocity vs time of the rigid slider}
\label{fig:velocity-vs-time-controlled-sliding}
\end{figure}

\FloatBarrier%
\subsection{Three bodies colliding}
\label{sec:three-bodies-colliding}

\begin{figure}[!htpb]
  \centering
  % \includegraphics[width=0.4\textwidth]{figures/mohseni_2021_free_sliding_on_a_slope_3d/velocity_vs_time}
  \caption{Schematic of the controlled rigid body sliding}
\label{fig:schematic-controlled-rigid-body-sliding}
\end{figure}

\begin{figure}[!htpb]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/amaro_2019_collision_between_three_rigid_cubes/Mohseni_Vyas/time0}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/amaro_2019_collision_between_three_rigid_cubes/Mohseni_Vyas/time1}
  \end{subfigure}

  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/amaro_2019_collision_between_three_rigid_cubes/Mohseni_Vyas/time2}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/amaro_2019_collision_between_three_rigid_cubes/Mohseni_Vyas/time3}
  \end{subfigure}
\caption{A dummy figure (To be fixed)}
\label{fig:snapshots-three-cubes-colliding}
\end{figure}
%

\FloatBarrier%
\subsection{Stack of cylinders}
\label{sec:stack-of-cylinders}

This test case is used to validate the current solid-solid contact force
model. A stack of cylinders initially at rest are allowed to settle under
gravity in a tank. This is simulated by Zhang (2011), where DEM is used. The
numerical parameters of the current test case are listed in
\Cref{tab:stack-of-cylinders}. The dimensions of the cylinder as well as the
tank are shown in figure (Ref the schematic figure).

\begin{table}[!ht]
  \centering
  \begin{tabular}[!ht]{ll}
    \toprule
    Quantity & Values\\
    \midrule
    $L$, length of the domain & 1 m \\
    Time of simulation & 2.5 s \\
    $c_s$ & 10 m/s \\
    $\rho_0$, reference density & 1 kg/m\textsuperscript{3} \\
    Reynolds number & 200 \& 1000 \\
    Resolution, $L/\Delta x_{\max} : L/\Delta x_{\min}$ & $[100:200]$ \& $[150:300]$\\
    Smoothing length factor, $h/\Delta x$ & 1.0\\
    \bottomrule
  \end{tabular}
  \caption{Parameters used for the Taylor-Green vortex problem.}%
  \label{tab:stack-of-cylinders}
\end{table}

\Cref{fig:snapshots-stack-of-cylinders} presents a set of snapshots
corresponding to the simulation of a stack of cylinders collapsing under
gravity using CTVF-DEM in comparison with the corresponding experimental
photos by Zhang. From the presented figure, the reproduced cylinder's
positions appear to be consistent with those observed in the experiment. From
\Cref{fig:snapshots-stack-of-cylinders}, the current solver has presented
proper level of stability.

\begin{figure}[!htpb]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/time0}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=0.75\textwidth]{images/stack_of_cylinders_experimental_images/time0}
  \end{subfigure}

  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/time1}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=0.75\textwidth]{images/stack_of_cylinders_experimental_images/time1}
  \end{subfigure}

  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/time2}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=0.75\textwidth]{images/stack_of_cylinders_experimental_images/time2}
  \end{subfigure}

  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/time3}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=0.75\textwidth]{images/stack_of_cylinders_experimental_images/time3}
  \end{subfigure}
\caption{A dummy figure (To be fixed)}
\label{fig:snapshots-stack-of-cylinders}
\end{figure}
%

\Cref{fig:x-com-stack-of-cylinders,fig:y-com-stack-of-cylinders} presents the
time histories of the x and y components of the center of mass of the
cylinders respectively as well as those from numerical simulations by
SPH-DCDEM as well as MPS-DEM with respect to those from the experiment Zhang.
From the presented figure, the effective center of mass of the cylinders is in
good agreement with the experiment.

\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/xcom}
  \caption{A dummy figure (To be fixed)}
\label{fig:x-com-stack-of-cylinders}
\end{figure}
\begin{figure}[!htpb]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/stack_of_cylinders_2d/Mohseni_Vyas/ycom}
  \caption{A dummy figure (To be fixed)}
\label{fig:y-com-stack-of-cylinders}
\end{figure}

\FloatBarrier%
\subsection{Falling solid in water}
\label{sec:falling-solid-in-water}

In this section, the rigid fluid coupling part of the current solver is
evaluated by simulation of a rigid cube falling in an hydrostatic tank (cite
experimental paper). The CTVF-DEM solver is employed to simulate water entry
of a rigid cube, which is studied experimentally by (cite the paper). The
numerical parameters of the current test case are listed in
\Cref{tab:stack-of-cylinders}. The dimensions of the schematic are shown in
figure.

\begin{table}[!ht]
  \centering
  \begin{tabular}[!ht]{ll}
    \toprule
    Quantity & Values\\
    \midrule
    $L$, length of the domain & 1 m \\
    Time of simulation & 2.5 s \\
    $c_s$ & 10 m/s \\
    $\rho_0$, reference density & 1 kg/m\textsuperscript{3} \\
    Reynolds number & 200 \& 1000 \\
    Resolution, $L/\Delta x_{\max} : L/\Delta x_{\min}$ & $[100:200]$ \& $[150:300]$\\
    Smoothing length factor, $h/\Delta x$ & 1.0\\
    \bottomrule
  \end{tabular}
  \caption{Parameters used for the Taylor-Green vortex problem.}%
  \label{tab:stack-of-cylinders}
\end{table}

A rigid cube of a side length of 30 mm enters the water initially at
hydrostatic state with a velocity of 30 $m/s$ in z-direction.
\Cref{fig:snapshots-falling-solid-in-water} presents a snapshots of the rigid
cube falling in an hydrostatic tank with the current solver as well as
WCSPH-DEM solver as well as the experimental result. From the presented figure
\Cref{fig:snapshots-falling-solid-in-water}, we can see that the pressure
distribution is smooth and the simulation is stable. A zoomed in view near the
rigid cube is presented in \cref{fig:snapshots-falling-solid-in-water-zoomed}
when simulated with WCSPH-DEM and CTVF-DEM. From
\cref{fig:snapshots-falling-solid-in-water-zoomed} we can see that the fluid
particle distribution around the body with CTVF scheme is uniform when
compared with WCSPH, thanks to the implemented transport velocity formulation.

\begin{figure}[!htpb]
  \centering
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time0}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time1}
  \end{subfigure}

  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time2}
  \end{subfigure}
  %
  \begin{subfigure}{0.48\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{figures/qiu_2017_falling_solid_in_water_2d/dx_0_002/time3}
  \end{subfigure}
\caption{A dummy figure (To be fixed)}
\label{fig:snapshots-falling-solid-in-water}
\end{figure}
